\section{Types} % based on type.logic
Type ID:\\
\tab \lstinline{type(id).}
\\
Size:\\
\tab \lstinline{type_size(id, size).}
\\
Unpadded size:\\
\tab \lstinline{type_unpaded_size(id, size).}

\subsection{Primitive Types} % based on primitive-type.logic
Primitive type:\\
\tab \lstinline{primitive_type(id).}
\\
Integer type:\\
\tab \lstinline{intger_type(id).}
\\
Floating point type:\\
\tab \lstinline{fp_type(id).}
\\
Void type:\\
\tab \lstinline{void_type(id).}
\\
Label type:\\
\tab \lstinline{label_type(id).}
% TODO: Metadata type
%\\
%Metadata type:\\
%\tab \lstinline{metadata_type(id).}
% TODO: Selectors (i.e. i1, i8, i32...)

\subsection{Derived Types} % based on derived-type.logic
Derived type:\\
\tab \lstinline{derived_type(id).}
\\
% Function type
Function type:\\
\tab \lstinline{function_type(id).}
\\
Function variable arguments:\\
\tab \lstinline{function_type_varargs(id).}
\\
Function return type:\\
\tab \lstinline{function_type_return(id, type).}
\\
Function parameter:\\
\tab \lstinline{function_type_param(id, index, type).}
\\
Number of function parameters:\\
\tab \lstinline{function_type_nparams(id, n).}
\\
% Pointer type
Pointer type:\\
\tab \lstinline{pointer_type(id).}
\\
Pointer component:\\
\tab \lstinline{pointer_type_component(id, type).}
\\
Pointer address:\\
\tab \lstinline{pointer_type_addr_space(id, addr).}
\\
Check if pointer is first class:\\
%\tab \lstinline{pointer_type_first_class(id, type) :- pointer_type_component(id, type), type_first_class(type).}
\tab \texttt{pointer\_type\_first\_class(id, type) :- \\
            \tab\tab pointer\_type\_component(id, type), \\
            \tab\tab type\_first\_class(type).}
\\
% TODO: rules for each type of pointer?
% Vector type
Vector type:\\
\tab \lstinline{vector_type(id).}
\\
Vector component:\\
\tab \lstinline{vector_type_component(id, type).}
\\
Vector size:\\
\tab \lstinline{vector_type_size(id, size).}
\\
% TODO: rules for each type of vector?
% Aggregate type
Aggregate type:\\
\tab \lstinline{aggregate_type(id).}
\\
% Array types
Array type:\\
\tab \lstinline{array_type(id).}
\\
Array component:\\
\tab \lstinline{array_type_component(id, type).}
\\
Array size:\\
\tab \lstinline{array_type_size(id, size).}
\\
% Struct type 
Struct type:\\
\tab \lstinline{struct_type(id).}
\\
Struct field:\\
\tab \lstinline{struct_type_field(id, index, field).}
\\
Number of struct field:\\
\tab \lstinline{struct_type_nfields(id, n).}
\\
Struct field byte offset:\\
\tab \lstinline{struct_type_field_offset(id, index, offset).}
\\
Struct field bit offset:\\
\tab \lstinline{struct_type_field_bit_offset(id, index, offset).}
% TODO: struct debug information
\\
Opaque type:\\
\tab \lstinline{opaque_type(id).}
\\
First class types:
\tab \lstinline{type_first_class(id) :- type(id), !function_type(id), !void_type(id).}
