\subsection{Memory Access and Addressing Operations}
The following set of relations represent instructions that read, write and allocate memory.

%%% Alloca instructions

\subsubsection{Allocate instruction} 
\noindent Instruction ID:
\texttt{alloca\_instruction(id).}

\noindent Alignment:
\texttt{alloca\_instruction\_alignment(id, align).}

\noindent Size:
\texttt{alloca\_instruction\_size(id, size).}

\noindent Type:
\texttt{alloca\_instruction\_type(id, type).}

 
%%% Load instructions

\subsubsection{Load instruction}
Instruction ID:
\texttt{load\_instruction(id).}

\noindent Alignment:
\texttt{load\_instruction\_alignment(id, align).}

\noindent Ordering:
\texttt{load\_instruction\_ordering(id, ord).}

\noindent Volatile:
\texttt{load\_instruction\_volatile(id).}

\noindent Atomic:
\texttt{load\_instruction\_atomic(Id) :- \\
        \tab store\_instruction\_ordering(Id, \_).}

\noindent Address:
\texttt{load\_instruction\_address(id, addr).}

%%% Store instructions 

\subsubsection{Store instruction}
Instruction ID:
\texttt{store\_instruction(id).}

\noindent Alignment:
\texttt{store\_instruction\_alignment(id, align).}

\noindent Ordering:
\texttt{store\_instruction\_ordering(id, ord).}

\noindent Volatile:
\texttt{store\_instruction\_volatile(id).}

\noindent Atomic:
\texttt{store\_instruction\_atomic(Id) :- \\
        \tab store\_instruction\_ordering(Id, \_).}

\noindent Value:
\texttt{store\_instruction\_value(id, value).}

\noindent Address:
\texttt{store\_instruction\_address(id, addr).}

%%% Fence instructions

\subsubsection{Fence instruction}
Instruction ID:
\texttt{fence\_instruction(id).}

\noindent Ordering:
\texttt{fence\_instruction\_ordering(id, order).}

%%% CmpXchg instructions

\subsubsection{Compare and exchange instruction}
Instruction ID:
\texttt{cmpxchg\_instruction(id).}

\noindent Ordering:
\texttt{cmpxchg\_instruction\_ordering(id, order).}

\noindent Volatility:
\texttt{cmpxchg\_instruction\_volatile(id).}

\noindent Address:
\texttt{cmpxchg\_instruction\_address(id, addr).}

\noindent Comparison:
\texttt{cmpxchg\_instruction\_cmp(id, cmp).}

\noindent New value:
\texttt{cmpxchg\_instruction\_new(id, value).}

%%% AtomicRMW instructions

\subsubsection{Atomic RMW instruction}
Instruction ID:
\texttt{atomicrmw\_instruction(id).}

\noindent Ordering:
\texttt{atomicrmw\_instruction\_ordering(id, order).}

\noindent Volatility:
\texttt{cmpxchg\_instruction\_volatile(id).}

\noindent Operation:
\texttt{atomicrmw\_instruction\_operation(id, op).}

\noindent Address:
\texttt{atomicrmw\_instruction\_address(id, addr).}

\noindent Value:
\texttt{atomicrmw\_instruction\_value(id, value).}

