\subsection{Terminator instructions}
The next set of relations represent the terminator instructions.
These are the instructions that end basic blocks.
They produce control flow.

\subsubsection{Return instruction}
Instruction ID:
\texttt{ret\_instruction(id).}

\noindent Terminator:
\texttt{terminator\_instruction(id) :- ret\_instruction(id).}

\noindent Return Value:
\texttt{ret\_instruction\_value(id, value).}

\noindent Void return:
\texttt{ret\_instruction\_void(id).}

% TODO: well formed rules
%\subsubsection{Well formed function rules}
%Well formed:
%\texttt{function\_wellformed(Id) :- function(Id), !function\_illformed(Id).}

\subsubsection{Branch instruction}
Instruction ID:
\texttt{br\_instruction(id).}

\noindent Terminator Instruction:
\texttt{terminator\_instruction(id).}

%\subsubsection{Conditional Branch}
\paragraph{Conditional Branch}
~\\Conditional branch instruction ID:
\texttt{br\_cond\_instruction(id).}

\noindent Condition:
\texttt{br\_cond\_instruction\_condition(id, cond).}

\noindent True case:
\texttt{br\_cond\_instruction\_iftrue(id, label).}

\noindent False case:
\texttt{br\_cond\_instruction\_iffalse(id, label).}

%\subsubsection{Unconditional Branch}
\paragraph{Unconditional Branch}
~\\\noindent Unconditional branch instruction ID:
\texttt{br\_uncond\_instruction(id).}

\noindent Destination:
\texttt{br\_cond\_instruction\_dest(id, label).}

\subsubsection{Unreachable instruction}
Instruction ID:
\texttt{unreachable\_instruction(id).}

\noindent If the instruction is unreachable, it is a terminator:\\
\tab \texttt{terminator\_instruction(Id) :- unreachable\_instruction(Id).}
